Object-based Auditory Scenes Similarity Retrieval and Classification With Scattering Transforms

### 2016-07-10 paper/structureScene.tex

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{pgf}
%\usepackage{tikz}
%\usetikzlibrary{arrows,positioning}
%\usetikzlibrary{arrows.meta}
\usepackage{url}
\usepackage{color}
\usepackage{graphicx}
\usepackage{xspace}
\newcommand*{\eg}{e.g.\@\xspace}
\newcommand*{\ie}{i.e.\@\xspace}
\newcommand*{\vs}{vs.\@\xspace}

@@

%\begin{figure}
%\begin{center}
%\begin{tikzpicture}
%\useasboundingbox[red] (-0.25, -0.5) rectangle (8.25, 2);
%\node (omlabel1) at (3.5, 1) {$t$};
%\draw[-{Latex[length=2mm]}] (0, 1) -- (omlabel1);
%\draw[-{Latex[length=2mm]}] (0, 1) -- (0, 2);
%\node[anchor=south west,inner sep=0] at (0, 0) {\includegraphics[height=2cm,width=3cm]{gammatone_Q8.png}};
%\node at (2, -0.25) {(a)};
%\node (omlabel2) at (8, 1) {$t$};
%\draw[-{Latex[length=2mm]}] (4.5, 1) -- (omlabel2);
%\draw[-{Latex[length=2mm]}] (4.5, 1) -- (4.5, 2);
%\node[anchor=south west,inner sep=0] at (4.5, 0) {\includegraphics[height=2cm,width=3cm]{gammatone_Q1.png}};
%\node at (6.5, -0.25) {(b)};
%\end{tikzpicture}
%\caption{
%\label{fig:gammatones}
%Gammatone wavelets $\psi(t)$ in the time domain with quality factors (a) $Q = 4$ and (b) $Q = 1$. Blue and red oscillations represent the real and imaginary parts. The orange envelope represents the complex modulus.}
%\end{center}
%\end{figure}

@@

\begin{table}
\begin{center}
\begin{tabular}{cccc}
                    & time-scattering & time-scattering & mfcc \\
                    & w/ log comp.    & w/o log comp.   &      \\
             \hline
early int. (linear)  & 66 (11)        & 62 (6)  & 46 (8)    \\
early int. (RBF)     & 60 (7)         & 57 (8)  & 60 (8)    \\
late int.  (linear)  & XX (XX)        & XX (XX) & XX (XX)   \\
late int.  (RBF)     & XX (XX)        & XX (XX) & XX (XX)   \\
ob-closest.          & XX (XX)        & XX (XX) & XX (XX)   \\
ob-averaged.         & XX (XX)        & XX (XX) & XX (XX)   \\
ob-weighted.         & XX (XX)        & XX (XX) & XX (XX)   \\
\end{tabular}
\caption{...}
\end{center}
\end{table}

>>>>

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
\usetikzlibrary{arrows.meta}
\usepackage{url}
\usepackage{color}
\usepackage{graphicx}
\usepackage{xspace}
\newcommand*{\eg}{e.g.\@\xspace}
\newcommand*{\ie}{i.e.\@\xspace}
\newcommand*{\vs}{vs.\@\xspace}

@@

\begin{figure}
\begin{center}
\begin{tikzpicture}
\useasboundingbox[red] (-0.25, -0.5) rectangle (8.25, 2);
\node (omlabel1) at (3.5, 1) {$t$};
\draw[-{Latex[length=2mm]}] (0, 1) -- (omlabel1);
\draw[-{Latex[length=2mm]}] (0, 1) -- (0, 2);
\node[anchor=south west,inner sep=0] at (0, 0) {\includegraphics[height=2cm,width=3cm]{gammatone_Q8.png}};
\node at (2, -0.25) {(a)};
\node (omlabel2) at (8, 1) {$t$};
\draw[-{Latex[length=2mm]}] (4.5, 1) -- (omlabel2);
\draw[-{Latex[length=2mm]}] (4.5, 1) -- (4.5, 2);
\node[anchor=south west,inner sep=0] at (4.5, 0) {\includegraphics[height=2cm,width=3cm]{gammatone_Q1.png}};
\node at (6.5, -0.25) {(b)};
\end{tikzpicture}
\caption{
\label{fig:gammatones}
Gammatone wavelets $\psi(t)$ in the time domain with quality factors (a) $Q = 4$ and (b) $Q = 1$. Blue and red oscillations represent the real and imaginary parts. The orange envelope represents the complex modulus.}
\end{center}
\end{figure}

@@

\begin{table}
\begin{center}
\begin{tabular}{cccc}
                    & time-scattering & time-scattering & mfcc \\
                    & w/ log comp.    & w/o log comp.   &      \\
             \hline
early int. (linear)  & 66 (11)        & 62 (6)  & 46 (8)    \\
early int. (RBF)     & 60 (7)         & 57 (8)  & 60 (8)    \\
late int.  (linear)  & 75 (5)         & 70 (8)  & 63 (8)   \\
late int.  (RBF)     & 78 (6)         & 73 (8)  & 72 (10)   \\
ob-closest.          & 66 (7)         & 58 (6)  & 56 (9)   \\
ob-averaged.         & 61 (7)         & 54 (8)  & 61 (9)   \\
ob-weighted.         & 54 (11)        & 43 (10) & 51 (15)   \\
\end{tabular}
\caption{...}
\end{center}
\end{table}
